Investigating the change of Toronto crime rates from 2014-2023

### 2024-01-25 Output/paper.qmd
2nd modified version

Toronto, Canada's largest city, hosts a population exceeding three million. Renowned for its robust economic landscape and cultural diversity, the city has concurrently experienced notable challenges in managing urban crime. In 2022, Toronto recorded a significant 15 percent increase in its crime rate, surpassing the national urban average by more than threefold \[\@citeCP24\].

>>>>

Toronto, Canada's largest city, hosts a population exceeding three million. Renowned for its robust economic landscape and cultural diversity, the city has concurrently experienced notable challenges in managing urban crime. In 2022, Toronto recorded a significant 15 percent increase in its crime rate, surpassing the national urban average by more than threefold [@citeCP24].
